Synthesizing Verified Components for Cyber Assured Systems Engineering \thanks{DISTRIBUTION STATEMENT A. Approved for public release.}

### 2022-03-14 paper/agree.tex
Add AGREE verification conditions

The goal of this section is to illustrate in more detail the process a system designer follows to add cyber requirements to the AGREE specifications and then automatically transform the system to insert the high-assurance components.
The AGREE specifications generated by the transforms for the high-assurance components are also explained.

\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree,numbers=left]
eq req : bool = event(AutomationRequest);
eq avl : bool = event(AirVehicleLocation);
eq wp : bool = event(Waypoint);
eq strt: bool = event(Start);
eq alrt : bool = event(Alert);

@@

>>>>

This section introduces the AGREE contract specification language through the cyber-hardened system of \figref{fig:hardened}.
It details the specification of that top-level system interface.
It then discusses the specifications for the filter and the monitor added by the transforms.

This section then formalizes AGREE's assume-guarantee reasoning by defining the set of verification conditions that AGREE must check.
The verification conditions succinctly summarize what in means when AGREE proves that a system implementation satisfies it specification.
These conditions are useful in understanding how the semantics in synthesis differ from those in the assume-guarantee reasoning in \secref{sec:semantics}.

\subsection{Contract Specification}
\newsavebox{\sw}
\begin{lrbox}{\sw}
\begin{lstlisting}[style=agree,numbers=left]
eq req : bool = event(AutomationRequest);
eq avl : bool = event(AirVehicleLocation);
eq wp : bool = event(Waypoint);
eq strt: bool = event(Start);
eq alrt : bool = event(Alert);

@@

\subsection{Verification Conditions}
\input{verification-conditions}
